Paradigms in Physics 2.0

### 2017-06-21 paper.tex
articulate ideas from meeting with Corinne

\section{Introduction}
The Paradigms in Physics program began around the time when our
current students were born~\cite{manogue2001paradigms}.  The time has
arrived for a change.  Over the years, we have identified a number of
problems in our curriculum that we were unable to address without
addressing the physics major curriculum as a whole.  In this paper, we
share the motivation for our Paradigms 2.0 effort, the process by
which we achieved consensus on an improved curriculum, and will give
a summary and a few highlights of the new program.

>>>>

\section{Introduction}
Basic Paradigms in Physics ideas:
\begin{enumerate}
\item Attention to sequencing of concepts (and articulating content
  learning goals)
\item Faculty buy in and understanding of the sequencing and goals
\item Active engagement
\end{enumerate}
\emph{This} is the Paradigms.  \emph{Explain why our 2.0 changes were
  made, how they addressed these principles.  (i.e. sophomore-year
  courses, math bits, giving students more electives as seniors) Also
  articulate the process (both 1.0 and 2.0) in terms of these big
  ideas.}

The Paradigms in Physics program began around the time when our
current students were born~\cite{manogue2001paradigms}.  The time has
arrived for a change.  Over the years, we have identified a number of
problems in our curriculum that we were unable to address without
addressing the physics major curriculum as a whole.  In this paper, we
share the motivation for our Paradigms 2.0 effort, the process by
which we achieved consensus on an improved curriculum, and will give
a summary and a few highlights of the new program.
